Uncovering underlying musical content in the temporal domain \\ \small Leveraging deep learning, inductive bias, and aural skills to learn embedding spaces for downstream MIR tasks

### 2023-03-12 introduction/Subsections/Motivation.tex
Updates from Overleaf

As a music lover, professional musician, and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition, the various techniques used to create musical works, and capturing underlying relationships among them. I am deeply interested in learning how to retrieve embedded information within music. The study of music structure analysis provides a means to systematically analyze and understand musical pieces. It has traditionally been approached through music theory, formal musical notation, musical analysis techniques, and machine learning, which I plan to blend.

@@

As a professional musician and music transcriber, I am interested in understanding how Deep Neural Networks (DNNs) filter musical features. In other words, I am eager to learn how DNNs listen to music.

>>>>

We argues that MIR research needs to incorporate a more balanced approach that considers the interdisciplinary nature of music and the importance of other domains beyond DSP.

As a music lover, professional musician, and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition, the various techniques used to create musical works, and capturing underlying relationships among them. I am deeply interested in learning how to retrieve embedded information within the music. The study of music structure analysis provides a means to analyze and understand musical pieces systematically. It has traditionally been approached through music theory, formal musical notation, musical analysis techniques, and machine learning, which I plan to blend.

@@

As a professional musician and music transcriber, I want to understand how Deep Neural Networks (DNNs) filter musical features. In other words, I am eager to learn how DNNs listen to music.

### 2023-03-12 introduction/Subsections/Objectives.tex
Updates from Overleaf

The purpose of this work is to generalize the fundamental harmonic structure of music to facilitate its application in downstream music information retrieval (MIR) tasks. Music, being a complex and fascinating art form, has been extensively studied by scholars and musicians for centuries. Understanding how music is organized and composed is critical, and music theory plays a vital role in this regard. Analyzing music structure poses a significant challenge as it comprises several elements, including melody, harmony, rhythm, and form.

In recent years, the utilization of neural networks has made it possible to create low-dimensional musical embeddings that capture crucial musical features and enable the computation of semantic similarity between musical passages. By acquiring an embedding function $f(x) \in \mathbb{R}^d$ that maps a given passage $x$ to a vector in the real space $\mathbb{R}^d$, researchers can measure the semantic similarity between two musical passages using the Euclidean distance, as represented by the formula $D_{i,j} = ||f(x_i) - f(x_j)||^2$. The effectiveness of such systems depends on the embedding space's ability to interpret music in a way that aligns with human perception. Therefore, a suitable embedding space is crucial to ensure that the output aligns with human expectations.

>>>>

This work aims to generalize the fundamental tonal-working structure of western-tradition music by learning and embedding space used to facilitate its application in downstream MIR tasks. Understanding how music is organized and composed is critical, and music theory plays a vital role in this regard.

In recent years, the utilization of neural networks has made it possible to create low-dimensional musical embeddings that capture crucial musical features and enable the computation of content-based similarity between musical passages. By acquiring an embedding function $f(x) \in \mathbb{R}^d$ that maps a given passage $x$ to a vector in the real space $\mathbb{R}^d$, researchers can measure the semantic similarity between two musical passages using the Euclidean distance, as represented by the formula $D_{i,j} = ||f(x_i) - f(x_j)||^2$. The effectiveness of such systems depends on the embedding space's ability to interpret music in a way that aligns with human perception. Therefore, a suitable embedding space is crucial to ensure that the output aligns with human expectations.
